---
title: "Politeness"
subtitle: "Detecting Politeness Features in Text"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Politeness}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, echo=F}
knitr::opts_chunk$set(comment = NA, echo=FALSE, message = FALSE, warning = FALSE)
library(politeness)

data("phone_offers")
data("feature_table") 
```

## Introduction 

Politeness is a universal dimension of human communication (Brown & Levenson, 1987). In practically all communication, a speaker can choose to be more or less polite to their audience.In this package, we porivde tools to measure the markers and effects of politeness in natural language.

## Motivation for package


## Politeness Features

The main l We borrow from existing research on the computational linguistics of politeness.

```{r}
knitr::kable(feature_table,align=rep("c",4),
col.names = c("Feature Name",
"POS Tags",
"Description",
"Example"))
```

## Data: phone_offers

This data base includes 


## Detecting politeness features

The function `politeness()`

```{r}
df_politeness <- politeness(phone_offers$message, binary=TRUE)
head(df_politeness[ , 7:12])
```

## Ploting politeness features

Politeness `data.frames` can be plotted by `politenessPlot()` 

```{r}

```

## Projecting politeness features

`politenessProjection()` 

## Getting more or least polite texts

`findPoliteTexts()`




